### 2024-02-19 paper_sisc_first_revision/localpsf.tex
edits during discussion between Nick and Noemi

Here we provide an overview of the operator approximation algorithm. Then, in the subsections (Sections \ref{sec:sample_point_selection}--\ref{sec:flip_eigs}) we present technical details of the algorithm that were not already covered in Section \ref{sec:prerequisites}.

%\subsection{Algorithm overview}
%\label{sec:algorithm_overview}

>>>>

Before presenting the technical details of the algorithm in Sections \ref{sec:sample_point_selection}--\ref{sec:flip_eigs}, we first provide an overview.
%Here we provide an overview of the operator approximation algorithm. 
%Then, in the subsections (Sections \ref{sec:sample_point_selection}--\ref{sec:flip_eigs}) we present technical details of the algorithm that were not already covered in Section \ref{sec:prerequisites}.

### 2024-02-19 revision/letter_revision.tex
edits during discussion between Nick and Noemi

Please find enclosed the revised manuscript ``Point spread function
approximation of high rank Hessians with locally supported
non-negative integral kernels'' by Nick Alger, Tucker Hartland, Noemi
Petra, and Omar Ghattas which we would like to resubmit to SISC in the
Numerical Algorithms for Scientific Computing section.

%
This cover letter is accompanied by a point-by-point list of responses
to the referees' comments. In addition, we have prepared a diff
document that highlights the differences between the initially
submitted and the new manuscript, where revisions are indicated by
color (blue represents new text, and red is deleted text). Please send
the diff document to the reviewers as well.

>>>>

Please find enclosed our revision to the manuscript ``Point spread function
approximation of high rank Hessians with locally supported
non-negative integral kernels'' by Nick Alger, Tucker Hartland, Noemi
Petra, and Omar Ghattas, which was submitted to SISC in the
Numerical Algorithms for Scientific Computing section.

%
This cover letter is accompanied by a point-by-point list of responses
to the referees' comments. In addition, we have prepared a diff
document that highlights the differences between the initially
submitted manuscript and the revised manuscript, where revisions are indicated by
color (blue represents new text, and red is deleted text). Please send
the diff document to the reviewers as well.
